RVD2: An ultra-sensitive variant detection model for low-depth targeted next-generation sequencing data

### 2013-12-08 doc/bioinformatics2013/RVD2.tex
typo corrected.

\paragraph{\textbf{GATK}}
We used GATK (v2.1-8) UnifiedGenotyper function to detect mutations on our synthetic data following the recommended workflow. Due to some format incompatibility, we applied Picard to format read group and GATK for realignment. In UnifiedGenotyper, -ploid (Number of samples in each pool $\times$ Sample Ploidy) was set at 1 because our synthetic data is haploid; -dcov was set at $10^6$ to avoid downsamplig coverage within GATK.

>>>>

\paragraph{\textbf{GATK}}
We used GATK (v2.1-8) UnifiedGenotyper function to detect mutations on our synthetic data following the recommended workflow. Due to some format incompatibility, we applied Picard to format read group and GATK for realignment. In UnifiedGenotyper, -ploid (Number of samples in each pool $\times$ Sample Ploidy) was set at 1 because our synthetic data is haploid; -dcov was set at $10^6$ to avoid downsampling coverage within GATK.
